Tabular Constraint Learning

### 2016-04-14 Paper/ECAI/tabular.tex
fixing the ordering issue

\newcommand{\constraints}{\ensuremath{\mathcal{C}}\xspace}
\newcommand{\format}[1]{\textit{#1}\xspace}
\newcommand{\generategroups}{\format{generateAssignments}}
\newcommand{\extractgroups}{\format{extractGroups}}
\newcommand{\extracttables}{\format{extractTables}}
\newcommand{\learnconstraints}{\format{learnConstraints}}
\newcommand{\findassignment}{\format{findSolutions}}
\newcommand{\postprocess}{\format{pruneRedundant}}
\newcommand{\constrainttorder}{\format{orderedConstraints}}

@@

\subsection{Constraint ordering} 
\sergey{refinement operator, we need emphasize it}
$\constrainttorder(\constraints,\dependencies)$ uses the DAG~\dependencies in Figure \ref{fig:learning_order} in the following way: all constraints are generated in the topological order of~\dependencies.
Solid edges point from more general to more specific constraints.
Therefore, if there is a solid edge from constraint~$C_1$ to constraint~$C_2$, then a set of subgroups satisfying~$C_2$ must contain the subgroups satisfying~$C_1$.

>>>>

\newcommand{\constraints}{\ensuremath{\mathcal{C}}\xspace}
\newcommand{\format}[1]{\textit{#1}\xspace}
\newcommand{\generategroups}{\format{generateAssignments}}
\newcommand{\extractgroups}{\format{extractGroups}}
\newcommand{\extracttables}{\format{extractTables}}
\newcommand{\learnconstraints}{\format{learnConstraints}}
\newcommand{\findassignment}{\format{findSolutions}}
\newcommand{\postprocess}{\format{pruneRedundant}}
\newcommand{\constrainttorder}{\format{generalityOrder}}

@@

\subsection{Constraint ordering} 
Since some constraints are more general than the other, we generate them in the generality order similar to the ILP techniques known as refinement operators \cite{luc_book}.

$\constrainttorder(\constraints,\dependencies)$ uses the DAG~\dependencies in Figure \ref{fig:learning_order} in the following way: all constraints are generated in the topological order of~\dependencies.
Solid edges point from more general to more specific constraints.
Therefore, if there is a solid edge from constraint~$C_1$ to constraint~$C_2$, then a set of subgroups satisfying~$C_2$ must contain the subgroups satisfying~$C_1$.
